Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
print(p)

>>>>

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in ", myplace, sep = ""))
print(p)
